\section{List of Participants}
%[DW] May as well keep same format as organising committee ? 
%\subsection*{Faculty}
%\begin{tabular}{ll}
%Bilbo Baggins & Professor, Dept. of Mechanical Engineering, University of Middle Earth \\
%Bilbo Baggins & Professor, Dept. of Mechanical Engineering, University of Middle Earth 
%\end{tabular}

%\subsection*{Doctoral Students}
%\begin{tabular}{ll}
%Bilbo Baggins &  Dept. of Mechanical Engineering, University of Middle Earth \\
%Bilbo Baggins &   Dept. of Mechanical Engineering, University of Middle Earth 
%\end{tabular}

\begin{longtable}{ll}
Dr. Naoya Abe & Tokyo Institute of Technology \\
Yasunori Aizawa & Tokyo Institute of Technology \\
Mr. Rei Akahoshi & Nagoya University \\
Mr. Kohei Aso & Kyushu University \\
Mr. Seiji Azukizawa & Kyushu University \\
Prof. Daniel Berrar & Tokyo Institute of Technology \\
Dr. Andrea Cammarano & University of Glasgow \\
Prof. James Cannon & Kyushu University \\
Prof. Qiang Chen & Kyushu University \\
Mr. Xiaosheng Chen & Tokyo Institute of Technology \\
Dr. Yonghwan Cho & Nagoya University \\
Mr. Chitiphon Chuaicham & Kyushu University \\
Prof. Jeffrey Cross & Tokyo Institute of Technology \\
Ms. Yuka Fujiki & Hokkaido University \\
Mr. Georg Graninger & Queen's University Belfast \\
Ms. Nao Hirakawa & Kyushu University \\
Prof. Yoshio Hisaeda & Kyushu University \\
Mr. Sung Hwang & Kyushu University \\
Prof. Shigekazu Ito & Tokyo Institute of Technology \\
Prof. Nobuyuki Iwatsuki & Tokyo Institute of Technology \\
Mr. Rikiya Kado & Tokyo Institute of Technology \\
Dr. Tetsuya Kadonosono & Tokyo Institute of Technology \\
Prof. Kuniyuki Kakushima & Tokyo Institute of Technology \\
Emeritus Prof. Kikuo Kishimoto & Tokyo Institute of Technology \\
Prof. Kiyonobu Kasama & Tokyo Institute of Technolog \\
Ms. Naoto Kimura & Tokyo Institute of Technology \\
Prof. Masamichi Kohno & Kyushu University \\
Mr. Nattanai Kunanusont & Tokyo Institute of Technology \\
Mr. Hikaru Kurasawa & Tokyo Institute of Technology \\
Dr. Mu Li & Tokyo Institute of Technology \\
Mr. Siyi Li & Tokyo Institute of Technology \\
Mr. Jun Liu & Imperial College London \\
Prof. Stephen Lyth & Kyushu University \\
Mr. Khajeh Manafi Pasha Siavash	& Kyushu University \\
Dr. Stephane Matsushita Yu & Tohoku University \\
Prof. Tsuyoshi Michinobu & Tokyo Institute of Technology \\
Prof. Yoshiko Miura & Kyushu University \\
Ms. Nanoka Miyahara & Kyushu University \\
Prof. Junko Morikawa & Tokyo Institute of Technology \\
Mr. Yuya Murakami & Tokyo Institute of Technology \\
Mr. Masamichi Murayama & Tokyo Institute of Technology \\
Prof. Nobuo Nakada & Tokyo Institute of Technology \\
Prof. Norihiro Nakai & Tokyo Institute of Technology \\
Mr. Yutaka Nakano & Tokyo Institute of Technology \\
Prof. Akinori Nishihara & Tokyo Institute of Technology \\
Dr. Takumi Ohashi & Tokyo Institute of Technology \\
Prof. Tatsuya Okubo & The University of Tokyo \\
Dr. John Shackleton & University of Glasgow \\
Prof. Yusuke Shimoyama & Tokyo Institute of Technology \\
Dr. Nobuaki Shiraki & Tokyo Institute of Technology \\
Prof. Masaharu Shiratani & Kyushu University \\
Mr. Dan Smith & Queen's University Belfast \\
Prof. Roderick A Smith & Imperial College London \\
Prof. David Stewart & Tokyo Institute of Technology \\
Dr. Yuko Suto & Tohoku University \\
Prof. Atsushi Takahashi & Tokyo Institute of Technology \\
Prof. Hiroshi Takamatsu & Kyushu University \\
Mr. Kazuma Tanaka & Kyushu University \\
Mr. Kazuki Tokumaru & Kyushu University \\
Prof. Yuji Wada & Tokyo Institute of Technology \\
Dr. Darren Wall & Kyushu University \\
Prof. Wen Wang & Queen Mary University of London \\
Dr. Ian Watson & University of Glasgow \\
Dr. Elizabeth Webeck & Tohoku University \\
Ms. Yuanhao Wu & Queen Mary University of London \\
Mr. Ji Xia & Tohoku University \\
Prof. Kousuke Yakubo & Hokkaido University \\
Prof. Akira Yamada & Tokyo Institute of Technology \\
Prof. Teppei Yamada & Kyushu University \\
Prof. Kazuhiro Yasuda & Kyushu University \\
Ms. Jaebong Yeon & Osaka University \\
Mr. Naoki Kumagai & Tohoku University \\

\end{longtable}
